%----------------------------------------------------------------------------------------
%	CERTIFICATE OF APPROVAL
%----------------------------------------------------------------------------------------

%put a tilte:
%title:Thesis examination information
%Subtitle: Submitted by: Name

%Degree name in Program name

\noindent
{\Large \ttitle} \newline
Submitted by \authorname \newline

\noindent
\degreename \hspace{0.07cm} in \subjectname

\vspace{1cm}

An oral defense of this thesis took place on October 19, 2018 in front of the following examining committee: 

      \begin{table}[h!]
      \centering
      %\setlength{\tabcolsep}{0.125cm}
      \caption*{Examining Committee}
        %\hspace*{-4.0cm}
         \scalebox{1.0}{
        \begin{tabular}{@{}ll@{}}
          \toprule
          Chair of Examining Committee     & Dr. Big Bird       \\
          Research Supervisor    &  Dr. Elmo     \\      
          Examining Committee Member & Dr. The Count \\
          Examining Committee Member & Dr. Oscar\\ 
          Thesis examiner & Dr. Bert, (Masters), affiliation \\
          External Examiner & Dr. Bert, affiliation \\
          \bottomrule
        \end{tabular}
        }
      \end{table}


The above committee determined that the thesis is acceptable in form and content and that a satisfactory knowledge of the field covered by the thesis was demonstrated by the candidate during an oral examination.  A signed copy of the Certificate of Approval is available from the School of Graduate and Postdoctoral Studies.

\cleardoublepage

%----------------------------------------------------------------------------------------
%	ABSTRACT PAGE
%----------------------------------------------------------------------------------------
\begin{abstract}
\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
The Thesis Abstract is written here (and usually kept to just this page). The page is kept centered vertically!

The abstract occupies a single page and provides a summary of the thesis outlining the problem, methods of investigation, main results and general conclusions. The abstract must give enough information about the thesis to allow a potential reader to decide whether or not to consult the complete work. It should not include graphs, charts, illustrations, tables or references.

The abstract of a master’s thesis must not exceed 150 words, while the abstract of a doctoral thesis may be up to 350 words. These guidelines will be strictly enforced, or so they say over at SGPS...

At the end of the Abstract should appear a list of keywords. 
\\[0.5cm]
\textbf{Keywords:} \LaTeX, UOIT, Thesis
\end{abstract}

%----------------------------------------------------------------------------------------
%	DECLARATION PAGE
%----------------------------------------------------------------------------------------
\begin{declaration}
\addchaptertocentry{\authorshipname} % Add the declaration to the table of contents
%\noindent I, \authorname, declare that this thesis titled, \enquote{\ttitle} and the work presented in it are my own. I confirm that:

\begin{itemize} 
\item I hereby declare that this thesis consists of original work of which I have authored. This is a true copy of the thesis, including any required final revisions, as accepted by my examiners.
\item I authorize the University of Ontario Institute of Technology to lend this thesis to other institutions or individuals for the purpose of scholarly research. I further authorize University of Ontario Institute of Technology to reproduce this thesis by photocopying or by other means, in total or in part, at the request of other institutions or individuals for the purpose of scholarly research. I understand that my thesis will be made electronically available to the public.\\
\end{itemize}

If your research need ethics approval this goes here. 
 
\noindent Signed:\\
\rule[0.5em]{25em}{0.5pt} % This prints a line for the signature
 
\noindent Date:\\
\rule[0.5em]{25em}{0.5pt} % This prints a line to write the date
\end{declaration}




%%----------------------------------------------------------------------------------------
%%	STATEMENT OF CONTRIBUTIONS
%%----------------------------------------------------------------------------------------
%
\begin{contributions}
\addchaptertocentry{\contributionsname} 

This section must include any contributing people or funding for the Thesis, talk with supervisor to ensure you have the correct statements. If you have published the work IT MUST be noted here, if you have not there is a sentence you can copy+paste into here from UOIT template.

From the Guidelines: In the case where a thesis includes papers co-authored by the candidate and others, the thesis must state explicitly who contributed to such work and the nature and extent of this contribution. The Supervisor(s) must attest to the accuracy of such statements about co-authorship at the oral examination.

\end{contributions}

%----------------------------------------------------------------------------------------
%	DEDICATION
%----------------------------------------------------------------------------------------

\dedicatory{For/Dedicated to/To my\ldots} 

\cleardoublepage
%----------------------------------------------------------------------------------------
%	QUOTATION PAGE
%----------------------------------------------------------------------------------------

\vspace*{0.2\textheight}

\noindent\enquote{\itshape 'You can't give her that!' she screamed. 'It's not safe!'\\ IT'S A SWORD, said the Hogfather. THEY'RE NOT MEANT TO BE SAFE.\\
'She's a child!' shouted Crumley.\\
IT'S EDUCATIONAL.\\
'What if she cuts herself?'\\
THAT WILL BE AN IMPORTANT LESSON..}\bigbreak
%
\hfill Terry Pratchett

\cleardoublepage


%----------------------------------------------------------------------------------------
%	ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------

\begin{acknowledgements}
\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
From the guidelines: This is a brief acknowledgment of assistance given to the candidate in his/her research and writing. The content and format of this page are up to the student.
\end{acknowledgements}